A Spatial AR System for Wide-area Axis-aligned Augmentation of Planar Scenes in Industrial Settings

### 2021-07-02 paper/elsarticle/elsarticle-template.tex
Update elsarticle-template.tex

Using the $X$- and $Y$-axes of an image of the scene as a proxy, our contribution is to propose a spatial AR system that produces the effect of keystone correction analytically, and in a manner aligning the axes of the augmentation with those of the proxy image. We achieve this by distorting the image to be projected using a plane-induced homography computed to produce the effect of projecting the image not from the actual projector viewpoint, but in accordance with the viewpoint of a \textit{virtual} projector (i) facing directly downwards to the scene plane and (ii) rotated to place the axes of the image plane of the virtual projector in line with those of the camera. This enables intuitive placement of augmentations in the scene, and eliminates the need for manual keystone correction. Moreover, a consequence of our approach is that our system is able to handle a projector equipped with a steerable mirror (without need for explicitly modeling the action of the steerable mirror on the projector), thereby enabling wide-area applications.

>>>>

Using the $X$- and $Y$-axes of an image of the scene as a proxy, our contribution is to propose a spatial AR system that produces the effect of keystone correction analytically, and in a manner aligning the axes of the augmentation with those of the proxy image. We achieve this by distorting the image to be projected using a plane-induced homography computed to produce the effect of projecting the image not from the actual projector viewpoint, but in accordance with the viewpoint of a \textit{virtual} projector (i) facing directly downwards to the scene plane and (ii) rotated to place the axes of the image plane of the virtual projector in line with those of the camera. This facilitates placement of augmentations by intuitively placing them in accordance with the axes of an image of the scene, and eliminates the need for manual keystone correction. Moreover, a consequence of our approach is that our system is able to handle a projector equipped with a steerable mirror (without need for explicitly modeling the action of the steerable mirror on the projector), thereby enabling wide-area factory floor applications.
